---
title: "Codebook"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Getting and Cleaning Data - Course Project

## Changes to the data

The following tasks were done on the original data set to create the clean data set:
* merged into one data set by combining training and test tests
* shortened to only include the measurements of the mean and standard deviation of each measurement
* renamed each activity in the data set using descriptive names
* dataset was relabelled with descriptive variable names
* took the average of each variable for each activity and each subject - the values created the independent tiny dataset

## Data Descriptions
###Identififiers
The second last column identifies the activity by name
The last column identifies the ID of the subject 


###Measurements
As mentioned above,the variables remaining are just the calculated means and standard deviations of all measurements in the data set: 

```{r}
colnames(all_data)
```

## Tiny dataset

The tiny dataset contains the same variable names shown. 


